Parallel Multi-objective Optimization Using Information Framework for Constructing Global Optimization Algorithms

### 2017-07-14 2017/URAL-PDC/u_pdc_paper.tex
u_pdc: fix missing h(x,y) definition

\section{Description of the Parallel Algorithm With Local Refinement}
\label{sec:algorithm}
Let us consider a scalarization scheme for the reduced problem (\(\ref{eq:problem}\)),
presented in~\cite{markinStrongin1993}. Let
\begin{equation}
  \varphi(x)=\max\{h(x,y):y\in [0,1]\},x\in [0,1].
\end{equation}
Let us consider a scalar problem
\begin{equation}
  \label{eq:aux_problem}
  \varphi^*=\min\{\varphi(x):x\in [0,1]\}.
\end{equation}

@@

\paragraph{Local refinement advantages.} In \cite{barkalovLebedev2016} the numerical
experiments demonstrating the speedup of convergence when using the local refinement
technique in the algorithm solving the scalar global optimization problems are presented. One
could expect similar results from the multi-objective algorithm as well. The multi-objective
algorithm with local refinement (MOAR) has been applied to the  Fonseca and Fleming
problem (\ref{eq:fonseca}) at \(n=2\). The parameters of the method were as follows:
\(\varepsilon=0.01,\;r=4,\;q=4,\;\alpha=15,\;p=1\). Before the method stops, 1176 iterations
have been executed, the number of found weakly optimal points was 90. At \(q=0\) (without the
local refinement) the method had performed 1484 iterations, the number of found weakly
optimal points was 93. In Fig. \ref{fig:fonseca_slater} the set \(S\) in the problem
(\ref{eq:fonseca}) and the numerical estimates of this one obtained at \(q=0\) (fig.
\ref{fig:fonseca_slater}.a) and \(q=4\) (fig. \ref{fig:fonseca_slater}.b) are presented. It is
evident also from fig. \ref{fig:fonseca_slater} that the approximate solution covers the whole
set of the weak-optimal solutions.

>>>>

\section{Description of the Parallel Algorithm With Local Refinement}
\label{sec:algorithm}
Let us consider a scalarization scheme for the reduced problem (\(\ref{eq:problem}\)),
presented in~\cite{markinStrongin1993}. Let
\begin{eqnarray*}
  \varphi(x)=\max\{h(x,y):y\in [0,1]\},x\in [0,1],\\
  h(x,y)=\max\{f_i(x)-f_i(y):1\leqslant i\leqslant\nu\}.
\end{eqnarray*}
Let us consider a scalar problem
\begin{equation}
  \label{eq:aux_problem}
  \varphi^*=\min\{\varphi(x):x\in [0,1]\}.
\end{equation}

@@

\paragraph{Local refinement advantages.} In \cite{barkalovLebedev2016} the numerical
experiments demonstrating the speedup of convergence when using the local refinement
technique in the algorithm solving the scalar global optimization problems are presented. One
could expect similar results from the multi-objective algorithm as well. The multi-objective
algorithm with local refinement (MOAR) has been applied to the  Fonseca and Fleming
problem (\ref{eq:fonseca}) at \(n=2\). The parameters of the method were as follows:
\(\varepsilon=0.01,\;r=4,\;q=4,\;\alpha=15,\;p=1\). Before the method stops, 1176 iterations
have been executed, the number of found weakly optimal points was 90. At \(q=0\) (without the
local refinement) the method had performed 1484 iterations, the number of found weakly
optimal points was 93. In Fig. \ref{fig:fonseca_slater} the set \(S\) in the problem
(\ref{eq:fonseca}) and the numerical estimates of this one obtained at \(q=0\) (Fig.
\ref{fig:fonseca_slater}.a) and \(q=4\) (Fig. \ref{fig:fonseca_slater}.b) are presented. It is
evident also from Fig. \ref{fig:fonseca_slater} that the approximate solution covers the whole
set of the weak-optimal solutions.
